Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2019-01-24 supplement.tex
Tons of stuffs

\begin{figure}[h!]
      \begin{center}
        %{\sf \bfseries A}\includegraphicstop[width=0.32\textwidth]{Figs/offset2}\hspace{.5cm}
        %{\sf \bfseries B}
        \includegraphicstop[width=0.8\textwidth]{Figs/energy_distribution}
      \end{center}
      \caption{%
        Targeting specific energies using multi-dimensional Boltzmann
        sampling. We show the Turner energy distributions for
        three target structures R1, R2 and R3. By
        targeting the respective free energies $(-40,-40,-20)$ and
        $(-20,-20,-20)$ for the target structures (annotated in red and
        blue, respectively), we demonstrate the
        effectivity of our adaptive multi-dimensional Boltzmann sampling
        procedure; moreover, for comparison, the distributions for uniform
        (U) and Boltzmann (B) samples---respectively associated with
        homogeneous weights $1$ and $e^\beta$.
%    ($\delta=0.05, \delta'=0.1, \gamma=1.1, \psi=20, n=1000$)
  }
  \label{appfig:energydist}
\end{figure}

>>>>

\begin{figure}[h!]
      \begin{center}
        %{\sf \bfseries A}\includegraphicstop[width=0.32\textwidth]{Figs/offset2}\hspace{.5cm}
        %{\sf \bfseries B}
        \includegraphicstop[width=0.8\textwidth]{Figs/energy_distribution}
      \end{center}
      \caption{%
        Targeting specific energies using multi-dimensional Boltzmann
        sampling. We show the Turner energy distributions for
        three target structures R1, R2 and R3. \revised{By
        targeting the respective free energies ($-40$, $-40$ and $-20$\,kcal/mol and $-20$,$-20$ and $-20$\,kcal/mol) for the target structures (annotated in red and
        blue, respectively), we demonstrate the
        effectivity of our adaptive multi-dimensional Boltzmann sampling
        procedure. Moreover, }for comparison, the distributions for uniform
        (U) and Boltzmann (B) samples---respectively associated with
        homogeneous weights $1$ and $e^\beta$.
%    ($\delta=0.05, \delta'=0.1, \gamma=1.1, \psi=20, n=1000$)
  }
  \label{appfig:energydist}
\end{figure}
